### 2019-11-08 inst/README.rmd
Changes provtools to MKLau in all docs

<!-- Code status -->
[![Build Status](https://travis-ci.org/ProvTools/Rclean.svg?branch=master)](https://travis-ci.org/ProvTools/Rclean) 
[![Coverage status](https://codecov.io/gh/provtools/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/provtools/Rclean?branch=master)

@@

- [Rclean](https://github.com/ProvTools/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results (aka. variables), large and/or
  complicated analytical scripts can be paired down to the essentials
  and easily re-factored to be more robust and easily shared.

>>>>

<!-- Code status -->
[![Build Status](https://travis-ci.org/MKLau/Rclean.svg?branch=master)](https://travis-ci.org/MKLau/Rclean) 
[![Coverage status](https://codecov.io/gh/MKLau/Rclean/branch/master/graph/badge.svg)](https://codecov.io/github/MKLau/Rclean?branch=master)

@@

- [Rclean](https://github.com/MKLau/Rclean) was created to help
  scientists more *easily* write "cleaner" code. 
- Written with research scientists that are results oriented in mind,
  the package's primary function provides a simple way to isolate the
  minimal code you need to produce a specific result, such as a
  statistical table or a figure.
- By focusing on specific results (aka. variables), large and/or
  complicated analytical scripts can be paired down to the essentials
  and easily re-factored to be more robust and easily shared.
